Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array

### 2016-05-17 ForegroundSimulations/ms.tex
Bold highlights to normal font, minor edits
From 314d0d4 (fgsim):
====================

In ms.tex,

(*) Revert bold font highlighting to normal font
(*) Change \tilde to \widetilde

Unaccounted for systematics from foregrounds and instruments can severely limit the sensitivity of current experiments from detecting redshifted 21~cm signals from the Epoch of Reionization (EoR). Upcoming experiments are faced with a challenge to deliver more collecting area per antenna element without degrading the data with systematics. This paper and its companions show that dishes are viable for achieving this balance using the Hydrogen Epoch of Reionization Array (HERA) as an example. Here, we specifically identify spectral systematics associated with the antenna power pattern as a significant detriment to all EoR experiments which causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes. A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas. Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation. We show HERA will not be impeded by such spectral systematics and demonstrate that even in a conservative scenario that does not perform removal of foregrounds, HERA will detect EoR signal in line-of-sight $k$-modes, $k_\parallel \gtrsim 0.2\,h$~Mpc$^{-1}$, with high significance. {\bf Under these conditions,} all baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.

@@

The most significant challenge to low frequency EoR observations arises from the extremely bright Galactic and extragalactic foreground synchrotron emission which are $\sim 10^4$ times stronger than the desired EoR signal \citep{dim02,ali08,ber09,ber10,gho12}. However, there are inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds \citep[see, e.g.,][]{fur04b,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}. {\bf For instance, the foregrounds have smooth spectrum and are not isotropic, whereas the EoR signal manifests with a fluctuating spectrum and statistical isotropy.}

When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, {\bf owing to its smooth spectrum}. {\bf On the other hand, the EoR power spectrum has spherical symmetry due to statistical isotropy and non-smooth spectrum}. The region of $k$-space excluding the {\it foreground wedge} is commonly referred to as the {\it EoR window} since it is expected to be relatively free of foreground contamination.

@@

Along with companion papers \citep{ewa16,neb16,pat16}, we focus on determining whether larger antenna elements can be viable for EoR experiments. In this paper, we explore the impact of chromaticity in the antenna power pattern on extending foreground power beyond the {\it wedge}. While highlighting the importance of such instrumental systematics on future EoR experiments, we demonstrate that the HERA instrument design {\bf planned} will detect the EoR signal with high significance. This will hold true when data is limited by foregrounds and systematics even in the most conservative scenario which involves neither foreground subtraction nor optimal analysis techniques but only relies on a simple spectral weighting scheme.

@@

\citet{deb16} describe the HERA instrument in detail while \citet{pob14} explored the range of astrophysical parameters that HERA can probe. We provide a summary of the instrument currently under construction {\bf in the South African Karoo Radio Astronomy Reserve}.

@@

HERA is deploying 14~m fixed zenith-pointing parabolic dishes that {\bf aim to} strike a balance between sensitivity and systematics \citep[][and this paper]{deb15,ewa16,neb16,pat16}. The large collecting area of a HERA element {\bf will yield} $\approx 5$ times the sensitivity of an MWA tile and more than 20 times that of a PAPER element.

@@

In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout that {\bf is} currently in use {\bf (see Figure~\ref{fig:HERA-19})}. Without loss of generality, the analysis and results in this paper will apply to the full proposed layout as well.

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{f1.eps}
  \caption{{\bf 19-element HERA layout used in this study, a subset of the full proposed 350-element layout. It is located in the South African Karoo Radio Astronomy Reserve. Each dish is 14~m across. The relative physical scale is illustrated by the group of people in this picture.}}
  \label{fig:HERA-19}
\end{figure}

@@

{\it Visibilities} measured by an interferometer are given by \citep{van34,zer38,tho01}:
\begin{align}\label{eqn:obsvis}
  V_b(f) &= \int\limits_\textrm{sky} A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif\Omega,
\end{align}
where, $\boldsymbol{b}$ is the vector joining antenna pairs (commonly referred to as the baseline vector), $\hat{\boldsymbol{s}}$ is the unit vector denoting direction on the sky, $f$ denotes frequency, $c$ is the speed of light, $\dif\Omega$ is the solid angle element to which $\hat{\boldsymbol{s}}$ is the unit normal vector, $I(\hat{\boldsymbol{s}},f)$ and $A(\hat{\boldsymbol{s}},f)$ are the sky brightness and antenna's directional power pattern, respectively, as a function of $\hat{\boldsymbol{s}}$ and $f$. The {\it delay spectrum}, $\tilde{V}_b(\tau)$, is defined as the inverse Fourier transform of $V_b(f)$ along the frequency coordinate:
\begin{align}\label{eqn:delay-transform}
  \tilde{V}_b(\tau) &\equiv \int V_b(f)\,W(f)\,e^{i2\pi f\tau}\,\dif f,
\end{align}
where, $W(f)$ is a spectral weighting function which can be chosen to control the quality of the delay spectrum \citep{ved12,thy13}, and $\tau$ represents the signal delay between antenna pairs:
\begin{equation}\label{eqn:delay}
  \tau = \frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}.
\end{equation}

The delay spectrum has a close resemblance to cosmological H{\sc i} spatial power spectrum and is defined as:
\begin{align}\label{eqn:delay-power-spectrum}
  P(\boldsymbol{b},k_\parallel) &\equiv |\tilde{V}_b(\tau)|^2\left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
\end{align}
with
\begin{align}
  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \label{eqn:kperp-baseline}\\
  k_\parallel &\equiv \frac{2\pi\,f_{21}H_0\,E(z)}{c(1+z)^2}\,\tau, \label{eqn:kprll-delay}
\end{align}
where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest-frame frequency of the 21~cm spin-flip transition of H{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology. $P(\boldsymbol{b},k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$. In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,h\,$km$\,$s$^{-1}\,$Mpc$^{-1}$ \citep{wmap9cosmo}. 
\begin{align}
  \Omega\Delta B &= \iint \left|A(\hat{\boldsymbol{s}},f)\,W(f)\right|^2\,\dif\Omega\,\dif f,
\end{align}
is related to the cosmic volume probed by the instrument \citep[see appendix of][]{par14}.

@@

In this paper, we investigate the spectral properties of the proposed HERA {\bf element (dish and feed)} design from a foreground contamination standpoint and the constraints they place on attenuation required to suppress reflections in the instrument.

@@

The High Frequency Structural Simulator (HFSS), {\bf a commercial finite element method solver for electromagnetic structures from Ansys,} was used to model the dish and its angular response used in this study. The HFSS model used prime focus optics with a 14~m faceted parabola with a spar $f/D$ ratio of 0.32.  The model has a 1~m central hole in the surface which is filled with a dielectric material similar to dry soil. The feed used a full PAPER dipole inside a cylindrical backplane. Dielectric stand-offs and supporting members were included. For the calculations, one pair of arms was excited using a modal port. {\bf Fig.~\ref{fig:HFSS-model} shows a schematic view of the dish-feed assembly modeled using HFSS.}

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{f2.eps}
  \caption{{\bf Schematic view of the HERA dish-feed assembly used in the HFSS model. The dish surface is modeled as a 14~m faceted parabola. The feed uses a PAPER dipole surrounded by a cylindrical backplane. A $f/D$ ratio of 0.32 is used. A length scale of 200~inches ($\approx 5$~m) is shown at the bottom for reference.}}
  \label{fig:HFSS-model}
\end{figure}

{\bf The dipoles were modeled with the actual materials used -- aluminum for the discs and copper for the arms and terminals. The dish and the backplane are actually meshed surfaces. For computational feasibility, they were modeled as aluminum surfaces in HFSS. At these frequencies, the cross-welded mesh electrical properties are well modeled as a good conductor like aluminum.}

These models cover a frequency range of 90--210~MHz in intervals of 1~MHz. {\bf They include multiple reflections between the dish and the feed but not those between dishes} \citep{deb16}.

@@

{\bf We use the foreground model of \citet{thy15a} wherein diffuse and point sources were shown to affect foreground contamination differently. The model for diffuse emission is obtained from \citet{deo08} and that for point sources} is obtained from a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz with a mean spectral index of -0.83. The diffuse sky model has an angular resolution of 13\farcm 74 and a spectral index estimated for every pixel.

@@

We use two models of EoR. In the first, simulations of the H{\sc i} signal were created using the publicly available 21cmFAST\footnote{\url{http://homepage.sns.it/mesinger/DexM\_\_\_21cmFAST.html}} code described in \citet{mes11}. The code uses the excursion set formalism of \citet{fur04a} to generate ionization and 21cm brightness fields for numerous redshifts. The model shown in this paper assumes the same fiducial values as in \citet{ewa16}: $T_\text{vir}^\text{min} = 2 \times 10^4$~K (virial temperature of minimum mass of dark matter halos that host ionizing sources), $\zeta = 20$ (ionization efficiency), and $R_\text{mfp}=15$~Mpc (mean free path of UV photons) which predicts the redshift of 50\% ionization (and hence a peak in the power spectrum signal) to be at $z=8.5$. The second EoR model is from the simulations described in detail in \citet{lid08}. Hereafter, we refer to these two as EoR models 1 and 2 respectively.

@@

{\bf Equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform} define} the interplay between foregrounds, {\bf the} antenna power pattern, and the mapping between geometric phases of baselines and delays. We discuss the spillover of foreground power beyond the horizon delay limits caused by the chromatic nature of the antenna power pattern.

@@

Fig.~\ref{fig:window-functions} shows the {\it Blackman-Harris} window (gray) and  the window in equation~\ref{eqn:bhw2} (black) in frequency (top) and their power responses in delay (bottom). In its Fourier domain, this window has a response obtained by squaring {\bf a} {\it Blackman-Harris} window response and thus increases the dynamic range further in the power response by another 100 -- 120~dB with $\epsilon\approx 42\%$ and $w_\textrm{ne} \approx 2.88$.

@@

{\bf It must be noted that in order to obtain this modified window function over a band of 100~MHz after convolution, the original {\it Blackman-Harris} window used in the convolution must occupy a band narrower than 100~MHz. This is why the modified window has a wider response in delay domain. This loss of delay-domain resolution, or equivalently, narrower effective bandwidth results in a slight reduction of noise sensitivity and delay resolution. While higher order powers could be used instead of the squared response we employ, there is a trade-off between the dynamic range, delay resolution, and sensitivity. A squared response was found to be sufficient for our purposes.}

In HERA-19 array layout, there are 30 unique baseline vectors and 8 unique baseline lengths. {\bf \citet{thy15a} showed that foreground contamination depends not only on the baseline length but also on its orientation, pointing direction on the sky, and whether the source of emission is diffuse or compact}. Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at {\bf certain chosen} pointings on the sky. {\bf It will be shown later in \S\ref{sec:baseline-RA} that choice of pointing is immaterial for HERA as long as pointings with the Galactic plane overhead are avoided}.

@@

\begin{figure*}[htb]
  \centering
  % \includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband_bhw2.0.eps}
  \includegraphics[width=\linewidth]{f4.eps}
  \caption{Foreground delay power spectra in units of K$^2 (h^{-1}$~Mpc$)^3$ on unique baseline lengths of HERA-19 at {\bf certain chosen} sky pointings. The baseline length and orientation (anti-clockwise from East) are annotated at the top right corner of each panel. Black, red and blue curves correspond to delay power spectra obtained with achromatic, {\it Airy} and chromatic simulated antenna beams respectively. The achromatic beam has no spectral structure, the simulated chromatic beam has maximum chromaticity while a nominal {\it Airy} pattern has intermediate level of chromaticity. The {\it pitchfork} effect is clearly visible as peaks around the horizon limits. With increase in chromaticity of the antenna beam the foreground spillover beyond the {\it foreground wedge} becomes progressively worse - the extent of foreground-spillover wings beyond the horizon limits (vertical dotted lines) and the amplitude of spillover beyond $k_\parallel\gtrsim 0.2\,h$~Mpc$^{-1}$ is most severe for the chromatic simulated beam, intermediate for an {\it Airy} pattern and negligible for an achromatic beam.}
  \label{fig:asm-dps-beam-chromaticity-baselines}
\end{figure*}

@@

Reflections shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause contamination in these critical $k_\parallel$-modes {\bf which is in addition to that already present due to spectral structures in the foregrounds and the instrument}. These delay shifts introduce ripples in the spectrum. The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, $I(\hat{\boldsymbol{s}},f)$, the baseline- and position-dependent frequency structure of the geometric phases, $e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}$, the spectral features in the antenna power pattern, $A(\hat{\boldsymbol{s}},f)$, besides any other spectral structures in the instrument unaccounted for. In $P(\boldsymbol{b},k_\parallel)$ defined in the Fourier domain, these factors have a convolving effect.

@@

Both EoR models were employed in this analysis to reduce the dependence of design specifications on any single model. However, we found similar results except for minor differences caused by {\bf relatively} small amplitude differences between the two EoR models {\bf for $|k_\parallel|>k_\textrm{p}$}. Hence, we only present results from using EoR model 1 at 150~MHz.

@@

\begin{figure}[htb]
  \centering
  % \includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
  \includegraphics[width=\linewidth]{f5.eps}
  \caption{Minimum required attenuation (in dB) for internal dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted). This is obtained on 14.6~m antenna spacing for EoR model 1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model. For EoR to be detectable in respective $k_\parallel$-modes despite these systematics, the attenuation of reflections must exceed these limits (outside the shaded regions).}
  \label{fig:fg-reflections-achrmbeam}
\end{figure}

@@

We note here that designing {\bf an antenna element whose beam} closely resembles a nominal {\it Airy} pattern will have a significantly higher tolerance for allowing antenna-to-antenna reflections and yet remain very effective for EoR signal detection. The HERA collaboration constantly pursues improvement of its {\bf antenna element} design to minimize limitations from such chromatic systematics.

@@

{\bf The HERA antenna beam model used accounts for chromaticity introduced due to reflections between the dish and the feed but not between dishes. Ignoring the latter,} we estimate the EoR-foreground dynamic range (ratio of EoR signal and foreground powers) {\bf achievable with HERA} for both EoR models in the presence of antenna beam chromaticity. In order to avoid signal evolution across the entire band, we use subbands in which EoR signal evolution is not expected to be significant. These subbands with $B_\textrm{eff}=10$~MHz are defined by spectral weights in equation~\ref{eqn:bhw2}. These subbands are centered at 150~MHz and 170~MHz to estimate EoR-foreground dynamic range at $z \approx 8.47$ and $z \approx 7.36$ respectively.

>>>>

Unaccounted for systematics from foregrounds and instruments can severely limit the sensitivity of current experiments from detecting redshifted 21~cm signals from the Epoch of Reionization (EoR). Upcoming experiments are faced with a challenge to deliver more collecting area per antenna element without degrading the data with systematics. This paper and its companions show that dishes are viable for achieving this balance using the Hydrogen Epoch of Reionization Array (HERA) as an example. Here, we specifically identify spectral systematics associated with the antenna power pattern as a significant detriment to all EoR experiments which causes the already bright foreground power to leak well beyond ideal limits and contaminate the otherwise clean EoR signal modes. A primary source of this chromaticity is reflections in the antenna-feed assembly and between structures in neighboring antennas. Using precise foreground simulations taking wide-field effects into account, we provide a framework to set cosmologically-motivated design specifications on these reflections to prevent further EoR signal degradation. We show HERA will not be impeded by such spectral systematics and demonstrate that even in a conservative scenario that does not perform removal of foregrounds, HERA will detect EoR signal in line-of-sight $k$-modes, $k_\parallel \gtrsim 0.2\,h$~Mpc$^{-1}$, with high significance. Under these conditions, all baselines in a 19-element HERA layout are capable of detecting EoR over a substantial observing window on the sky.

@@

The most significant challenge to low frequency EoR observations arises from the extremely bright Galactic and extragalactic foreground synchrotron emission which are $\sim 10^4$ times stronger than the desired EoR signal \citep{dim02,ali08,ber09,ber10,gho12}. However, there are inherent differences in spatial isotropy and spectral smoothness between the EoR signal and the foregrounds \citep[see, e.g.,][]{fur04b,mor04,zal04,san05,fur06,mcq06,mor06,wan06,gle08}. For instance, the foregrounds have smooth spectrum and are not isotropic, whereas the EoR signal manifests with a fluctuating spectrum and statistical isotropy.

When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} bounded by the horizon limits \citep{par12b}, owing to its smooth spectrum. On the other hand, the EoR power spectrum has spherical symmetry due to statistical isotropy and non-smooth spectrum. The region of $k$-space excluding the {\it foreground wedge} is commonly referred to as the {\it EoR window} since it is expected to be relatively free of foreground contamination.

@@

Along with companion papers \citep{ewa16,neb16,pat16}, we focus on determining whether larger antenna elements can be viable for EoR experiments. In this paper, we explore the impact of chromaticity in the antenna power pattern on extending foreground power beyond the {\it wedge}. While highlighting the importance of such instrumental systematics on future EoR experiments, we demonstrate that the HERA instrument design planned will detect the EoR signal with high significance. This will hold true when data is limited by foregrounds and systematics even in the most conservative scenario which involves neither foreground subtraction nor optimal analysis techniques but only relies on a simple spectral weighting scheme.

@@

\citet{deb16} describe the HERA instrument in detail while \citet{pob14} explored the range of astrophysical parameters that HERA can probe. We provide a summary of the instrument currently under construction in the South African Karoo Radio Astronomy Reserve.

@@

HERA is deploying 14~m fixed zenith-pointing parabolic dishes that aim to strike a balance between sensitivity and systematics \citep[][and this paper]{deb15,ewa16,neb16,pat16}. The large collecting area of a HERA element will yield $\approx 5$ times the sensitivity of an MWA tile and more than 20 times that of a PAPER element.

@@

In this study, we use the HERA-19 hexagonal array layout, a small subset of the planned layout that is currently in use (see Figure~\ref{fig:HERA-19}). Without loss of generality, the analysis and results in this paper will apply to the full proposed layout as well.

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{f1.eps}
  \caption{19-element HERA layout used in this study, a subset of the full proposed 350-element layout. It is located in the South African Karoo Radio Astronomy Reserve. Each dish is 14~m across. The relative physical scale is illustrated by the group of people in this picture.}
  \label{fig:HERA-19}
\end{figure}

@@

{\it Visibilities} measured by an interferometer are given by \citep{van34,zer38,tho01}:
\begin{align}\label{eqn:obsvis}
  V_b(f) &= \int\limits_\textrm{sky} A(\hat{\boldsymbol{s}},f)\,I(\hat{\boldsymbol{s}},f)\,e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}\,\dif\Omega,
\end{align}
where, $\boldsymbol{b}$ is the vector joining antenna pairs (commonly referred to as the baseline vector), $\hat{\boldsymbol{s}}$ is the unit vector denoting direction on the sky, $f$ denotes frequency, $c$ is the speed of light, $\dif\Omega$ is the solid angle element to which $\hat{\boldsymbol{s}}$ is the unit normal vector, $I(\hat{\boldsymbol{s}},f)$ and $A(\hat{\boldsymbol{s}},f)$ are the sky brightness and antenna's directional power pattern, respectively, as a function of $\hat{\boldsymbol{s}}$ and $f$. The {\it delay spectrum}, $\widetilde{V}_b(\tau)$, is defined as the inverse Fourier transform of $V_b(f)$ along the frequency coordinate:
\begin{align}\label{eqn:delay-transform}
  \widetilde{V}_b(\tau) &\equiv \int V_b(f)\,W(f)\,e^{i2\pi f\tau}\,\dif f,
\end{align}
where, $W(f)$ is a spectral weighting function which can be chosen to control the quality of the delay spectrum \citep{ved12,thy13}, and $\tau$ represents the signal delay between antenna pairs:
\begin{equation}\label{eqn:delay}
  \tau = \frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}.
\end{equation}

The delay spectrum has a close resemblance to cosmological H{\sc i} spatial power spectrum and is defined as:
\begin{align}\label{eqn:delay-power-spectrum}
  P(\boldsymbol{b},k_\parallel) &\equiv |\widetilde{V}_b(\tau)|^2\left(\frac{1}{\Omega\Delta B}\right)\left(\frac{D^2\Delta D}{\Delta B}\right)\left(\frac{\lambda^2}{2k_\textrm{B}}\right)^2,
\end{align}
with
\begin{align}
  \boldsymbol{k}_\perp &\equiv \frac{2\pi(\frac{\boldsymbol{b}}{\lambda})}{D}, \label{eqn:kperp-baseline}\\
  k_\parallel &\equiv \frac{2\pi\,f_{21}H_0\,E(z)}{c(1+z)^2}\,\tau, \label{eqn:kprll-delay}
\end{align}
where, $\Delta B$ is the bandwidth, $\lambda$ is the wavelength of the band center, $k_\textrm{B}$ is the Boltzmann constant, $\boldsymbol{k}_\perp$ and $k_\parallel$ are the transverse (on the sky) and line-of-sight (into the sky) wavenumbers respectively, $f_{21}$ is the rest-frame frequency of the 21~cm spin-flip transition of H{\sc i}, $z$ is the redshift, $D\equiv D(z)$ is the transverse comoving distance, $\Delta D$ is the comoving depth along the line of sight corresponding to $\Delta B$, and $h$, $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology. $P(\boldsymbol{b},k_\parallel)$ is in units of K$^2 (h^{-1}$~Mpc$)^3$. In this paper, we use $\Omega_\textrm{M}=0.27$, $\Omega_\Lambda=0.73$, $\Omega_\textrm{K}=1-\Omega_\textrm{M}-\Omega_\Lambda$, $H_0=100\,h\,$km$\,$s$^{-1}\,$Mpc$^{-1}$ \citep{wmap9cosmo}. 
\begin{align}
  \Omega\Delta B &= \iint \left|A(\hat{\boldsymbol{s}},f)\,W(f)\right|^2\,\dif\Omega\,\dif f,
\end{align}
is related to the cosmic volume probed by the instrument \citep[see appendix of][]{par14}.

@@

In this paper, we investigate the spectral properties of the proposed HERA element (dish and feed) design from a foreground contamination standpoint and the constraints they place on attenuation required to suppress reflections in the instrument.

@@

The High Frequency Structural Simulator (HFSS), a commercial finite element method solver for electromagnetic structures from Ansys, was used to model the dish and its angular response used in this study. The HFSS model used prime focus optics with a 14~m faceted parabola with a spar $f/D$ ratio of 0.32.  The model has a 1~m central hole in the surface which is filled with a dielectric material similar to dry soil. The feed used a full PAPER dipole inside a cylindrical backplane. Dielectric stand-offs and supporting members were included. For the calculations, one pair of arms was excited using a modal port. Fig.~\ref{fig:HFSS-model} shows a schematic view of the dish-feed assembly modeled using HFSS.

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{f2.eps}
  \caption{Schematic view of the HERA dish-feed assembly used in the HFSS model. The dish surface is modeled as a 14~m faceted parabola. The feed uses a PAPER dipole surrounded by a cylindrical backplane. A $f/D$ ratio of 0.32 is used. A length scale of 200~inches ($\approx 5$~m) is shown at the bottom for reference.}
  \label{fig:HFSS-model}
\end{figure}

The dipoles were modeled with the actual materials used -- aluminum for the discs and copper for the arms and terminals. The dish and the backplane are actually meshed surfaces. For computational feasibility, they were modeled as aluminum surfaces in HFSS. At these frequencies, the cross-welded mesh electrical properties are well modeled as a good conductor like aluminum.

These models cover a frequency range of 90--210~MHz in intervals of 1~MHz. They include multiple reflections between the dish and the feed but not those between dishes \citep{deb16}.

@@

We use the foreground model of \citet{thy15a} wherein diffuse and point sources were shown to affect foreground contamination differently. The model for diffuse emission is obtained from \citet{deo08} and that for point sources is obtained from a combination of the NRAO VLA Sky Survey \citep[NVSS;][]{con98} at 1.4~GHz and the Sydney University Molonglo Sky Survey \citep[SUMSS;][]{boc99,mau03} at 843~MHz with a mean spectral index of -0.83. The diffuse sky model has an angular resolution of 13\farcm 74 and a spectral index estimated for every pixel.

@@

We use two models of EoR. In the first, simulations of the H{\sc i} signal were created using the publicly available 21cmFAST\footnote{\url{http://homepage.sns.it/mesinger/DexM\_\_\_21cmFAST.html}} code described in \citet{mes11}. The code uses the excursion set formalism of \citet{fur04a} to generate ionization and 21cm brightness fields for numerous redshifts. The model shown in this paper assumes the same fiducial values as in \citet{ewa16}: $T_\text{vir}^\text{min} = 2 \times 10^4$~K (virial temperature of minimum mass of dark matter halos that host ionizing sources), $\zeta = 20$ (ionization efficiency), and $R_\text{mfp}=15$~Mpc (mean free path of UV photons) which predicts the redshift of 50\% ionization (and hence a peak in the power spectrum signal) to be at $z=8.5$. The second EoR model is from the simulations described in detail in \citet{lid08}. Hereafter, we refer to these two as EoR models~1 and 2 respectively.

@@

Equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform} define the interplay between foregrounds, the antenna power pattern, and the mapping between geometric phases of baselines and delays. We discuss the spillover of foreground power beyond the horizon delay limits caused by the chromatic nature of the antenna power pattern.

@@

Fig.~\ref{fig:window-functions} shows the {\it Blackman-Harris} window (gray) and  the window in equation~\ref{eqn:bhw2} (black) in frequency (top) and their power responses in delay (bottom). In its Fourier domain, this window has a response obtained by squaring a {\it Blackman-Harris} window response and thus increases the dynamic range further in the power response by another 100 -- 120~dB with $\epsilon\approx 42\%$ and $w_\textrm{ne} \approx 2.88$.

@@

It must be noted that in order to obtain this modified window function over a band of 100~MHz after convolution, the original {\it Blackman-Harris} window used in the convolution must occupy a band narrower than 100~MHz. This is why the modified window has a wider response in delay domain. This loss of delay-domain resolution, or equivalently, narrower effective bandwidth results in a slight reduction of noise sensitivity and delay resolution. While higher order powers could be used instead of the squared response we employ, there is a trade-off between the dynamic range, delay resolution, and sensitivity. A squared response was found to be sufficient for our purposes.

In HERA-19 array layout, there are 30 unique baseline vectors and 8 unique baseline lengths. \citet{thy15a} showed that foreground contamination depends not only on the baseline length but also on its orientation, pointing direction on the sky, and whether the source of emission is diffuse or compact. Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds on the 8 unique baseline lengths obtained with the aforementioned models for power pattern at certain chosen pointings on the sky. It will be shown later in \S\ref{sec:baseline-RA} that choice of pointing is immaterial for HERA as long as pointings with the Galactic plane overhead are avoided.

@@

\begin{figure*}[htb]
  \centering
  % \includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband_bhw2.0.eps}
  \includegraphics[width=\linewidth]{f4.eps}
  \caption{Foreground delay power spectra in units of K$^2 (h^{-1}$~Mpc$)^3$ on unique baseline lengths of HERA-19 at certain chosen sky pointings. The baseline length and orientation (anti-clockwise from East) are annotated at the top right corner of each panel. Black, red and blue curves correspond to delay power spectra obtained with achromatic, {\it Airy} and chromatic simulated antenna beams respectively. The achromatic beam has no spectral structure, the simulated chromatic beam has maximum chromaticity while a nominal {\it Airy} pattern has intermediate level of chromaticity. The {\it pitchfork} effect is clearly visible as peaks around the horizon limits. With increase in chromaticity of the antenna beam the foreground spillover beyond the {\it foreground wedge} becomes progressively worse - the extent of foreground-spillover wings beyond the horizon limits (vertical dotted lines) and the amplitude of spillover beyond $k_\parallel\gtrsim 0.2\,h$~Mpc$^{-1}$ is most severe for the chromatic simulated beam, intermediate for an {\it Airy} pattern and negligible for an achromatic beam.}
  \label{fig:asm-dps-beam-chromaticity-baselines}
\end{figure*}

@@

Reflections shift the measured foreground power to higher modes in $\tau$ (or in $k_\parallel$) and thus cause contamination in these critical $k_\parallel$-modes which is in addition to that already present due to spectral structures in the foregrounds and the instrument. These delay shifts introduce ripples in the spectrum. The net chromaticity in the measurements is the product of spectral structure arising out of the intrinsic nature of foreground emission, $I(\hat{\boldsymbol{s}},f)$, the baseline- and position-dependent frequency structure of the geometric phases, $e^{-i2\pi f\frac{\boldsymbol{b}\cdot\hat{\boldsymbol{s}}}{c}}$, the spectral features in the antenna power pattern, $A(\hat{\boldsymbol{s}},f)$, besides any other spectral structures in the instrument unaccounted for. In $P(\boldsymbol{b},k_\parallel)$ defined in the Fourier domain, these factors have a convolving effect.

@@

Both EoR models were employed in this analysis to reduce the dependence of design specifications on any single model. However, we found similar results except for minor differences caused by relatively small amplitude differences between the two EoR models at $|k_\parallel|>k_\textrm{p}$. Hence, we only present results from using EoR model~1 at 150~MHz.

@@

\begin{figure}[htb]
  \centering
  % \includegraphics[width=\linewidth]{spec_on_achrmbeam_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
  \includegraphics[width=\linewidth]{f5.eps}
  \caption{Minimum required attenuation (in dB) for internal dish-feed reflections required to keep the reflected foreground power below EoR H{\sc i} signal power for all $k_\parallel$-modes greater than $0.1\,h$~Mpc$^{-1}$ (solid), $0.15\,h$~Mpc$^{-1}$ (dashed) and $0.2\,h$~Mpc$^{-1}$ (dotted). This is obtained on 14.6~m antenna spacing for EoR model~1 at 150~MHz ($z\approx 8.47$) and foreground power obtained with an achromatic antenna beam model. For EoR to be detectable in respective $k_\parallel$-modes despite these systematics, the attenuation of reflections must exceed these limits (outside the shaded regions).}
  \label{fig:fg-reflections-achrmbeam}
\end{figure}

@@

We note here that designing an antenna element whose beam closely resembles a nominal {\it Airy} pattern will have a significantly higher tolerance for allowing antenna-to-antenna reflections and yet remain very effective for EoR signal detection. The HERA collaboration constantly pursues improvement of its antenna element design to minimize limitations from such chromatic systematics.

@@

The HERA antenna beam model used accounts for chromaticity introduced due to reflections between the dish and the feed but not between dishes. Ignoring the latter, we estimate the EoR-foreground dynamic range (ratio of EoR signal and foreground powers) achievable with HERA for both EoR models in the presence of antenna beam chromaticity. In order to avoid signal evolution across the entire band, we use subbands in which EoR signal evolution is not expected to be significant. These subbands with $B_\textrm{eff}=10$~MHz are defined by spectral weights in equation~\ref{eqn:bhw2}. These subbands are centered at 150~MHz and 170~MHz to estimate EoR-foreground dynamic range at $z \approx 8.47$ and $z \approx 7.36$ respectively.
